---
format: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file instead. -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
	collapse = TRUE,
	comment = "#>",
	fig.path = "README-",
	fig.retina = 3
)

box::use(
	mime,
	markdown,
	rmarkdown,
	emoji,
	yaml
)
```

# Pytorch test

<!-- badges: start -->
<!-- badges: end -->

### `r emoji::emoji_glue(":handshake::snake:")`: Note on "cooperative cobra" project name

I wasn't sure what to name this project or what it would be about, only that
I wanted to learn Pytorch. So I used [**codename**](https://svmiller.com/codename/)
to generate an  [Ubuntu-style](https://wiki.ubuntu.com/DevelopmentCodeNames)
working name for the project.

```{r codename, eval = FALSE}
library(codename)
codename_message()
#> code name generated by {codename} v.0.4.0

codename(seed = 31034987, type = "ubuntu")
#> [1] "cooperative cobra"
```

## Licenses

**Text and figures:** all text and images I create in this repository are
licensed under the Creative Commons Attribution-ShareAlike 4.0 International
License, [CC BY-SA 4.0](https://creativecommons.org/licenses/by-sa/4.0/).

**Code:** all code created by me is licensed under the GNU Affero General
Public License, [AGPL 3.0](LICENSE.md).

## Contributions and Contact Info

As this is a learning experience for me, I currently do not intend to accept
contributions. However, if you want to get in touch with me about this
repository (or anything else), please see my website for contact information:
[https://wzbillings.com](https://wzbillings.com).

<!-- END OF FILE -->
